Titeln på avhandlingens språk

### 2023-02-16 body/part1/overview/extending-wca.tex
model

\todo[inline]{Probably needs to repeat a discussion on why the new model is necessary, in a shorter summarized form.
This discussion should first be presented at the beginning of this section however.}

As discussed in \cref{impact:results}, the execution time for a step depends not only on the most recent perceived \gls{TTF}, but also on how long the system has been in the current level of responsiveness.
Moreover, as shown in \cref{fig:prevblockvsexectime}, the effects of reduced system responsiveness on generated execution times must be taken into consideration even after the system transitions into a more responsive state.
All of these effects are also modulated by neuroticism, adding both another layer of complexity and a means of parameterizing the model.

Our timing model produces realistic execution times for each step, according to the above effects.
We achieve this through the following design:

>>>>

Our current model of human behavior has a limitation that we need to address.
The model we have discussed so far emulates a rigid and unyielding human who is not affected by low responsiveness in the system.
This is not an accurate representation of real human behavior, and in the following we present a more realistic human model that takes into consideration the perceived feedback latency and its effects on human reactions.

Our new model is based on the comprehensive study of human behavior in the presence of feedback latency outlined in \cref{paper:olguinmunoz2021impact}, and has significant implications for the optimization of edge computing systems.
By incorporating a more accurate representation of human behavior into our methodology, we can better assess the impact of system design choices on the end-user experience.
This, in turn, enables future research into optimization strategies that are more effective at improving the overall quality of service for edge computing applications.

\medskip
As discussed in \cref{impact:results}, the execution time for a step depends not only on the most recent perceived \gls{TTF}, but also on how long the system has been in the current level of responsiveness.
Moreover, as shown in \cref{fig:prevblockvsexectime}, the effects of reduced system responsiveness on generated execution times must be taken into consideration even after the system transitions into a more responsive state.
All of these effects are also modulated by neuroticism, adding both another layer of complexity and a means of parameterizing the model.

Our new timing model produces realistic execution times for each step, according to the above effects.
We achieve this through the following design:
